Priors

### 2023-06-24 reports/priors.Rmd
add priors figures on beta distributions by state

library(tidyverse)
library(targets)
library(here)
library(latex2exp)

@@

>>>>

library(tidyverse)
library(targets)
library(here)
library(latex2exp)
library(viridis)

@@

## Distributions of $\beta$ by State

# raw ctis data

ctis_raw <- readRDS(here('data/data_raw/ctis_all_states.RDS'))

states_keep <- ctis_smoothed  %>%
  filter(keep) %>% pull(state) %>% unique()

ctis <- ctis_raw %>%
  select(signal, state=geo_value, date, value) %>%
  pivot_wider(names_from=signal, values_from=value) %>%
  filter(state %in% states_keep) %>%
  mutate(beta=smoothed_wscreening_tested_positive_14d/
           smoothed_wtested_positive_14d,
         state=toupper(state))

```{r ctis-by-state, fig.cap ="Since $\\beta$ represents the ratio of $\\Pr(\\text{test}_+|\\text{untested}, S_0)$ to $\\Pr(\\text{test}_+|\\text{tested})$, we estimate $\\beta$ from the COVID-19 Trends and Impact Survey as the ratio of the screening test positivity over the overall test positivity. Here, we consider the 2.5\\% and 97.5\\% percentiles and mean for each state. Most have a mean near $20%$.", fig.width=9}

ctis %>%
  group_by(state) %>%
  summarize(median = median(beta, na.rm=TRUE),
            mean = mean(beta, na.rm=TRUE),
            q1 = quantile(beta, .025,  na.rm=TRUE),
            q2 = quantile(beta, .975,  na.rm=TRUE)) %>%
  ggplot(aes(x= fct_reorder(state, mean, .desc=TRUE),
             y = mean)) +
  geom_errorbar(aes(ymin=q1,ymax=q2),width=.2) +
  geom_point(color="darkred", size=2) +
  scale_y_continuous(n.breaks=10) +
  labs(y= TeX("Empirical Estimates of $\\beta$"),
       x="State",
       title = TeX("Empirical Estimates of $\\beta$ from the COVID-19 Trends and Impact Survey"),
       subtitle = "2.7% Percentile, 97.5% Percentile, and Mean By State" ) +
  theme_c(axis.title=element_text(size=12))

ggsave(here("figures/emp-estimate-beta-dist-by-state.pdf"))

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c()

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c() +
  facet_wrap(~state)
